Forecasting the United States 2024 Presidential Election

### 2024-11-04 paper/paper.qmd

=======
## Analysis into a Pollster's Methodology

@@

Given a budget of $100k and the necessary resources, the idealized methodology for a survey that aims to forecast the results of the US election should be one that targets the states of interest with higher accuracy. Historically, certain states have very strong and consistent party preferences; for example, we can be almost entirely certain even without conducting any current research that California would be voting Democrat, simply because this has been how they voted in the past eight elections [@blueredstate]. Out of the 51 states, there are 20 states which voted for the same party each time in the past nine elections [@blueredstate]. On the other hand, there are seven states which have voted for each party three of more times——these would be the states of greater interest to us [@blueredstate]. Resources can be conserved by focussing our sampling and polling efforts on swing states where there is a greater uncertainty in vote outcome.

>>>>

## Analysis into a Pollster's Methodology {#sec-pollster-analysis}

@@

Given a budget of $100k and the necessary resources, the idealized methodology for a survey that aims to forecast the results of the US election should be one that uses quota sampling and the probability proportionate to size method to target the states of interest specifically. Historically, certain states have very strong and consistent party preferences; for example, we can be almost entirely certain even without conducting any current research that California would be voting Democrat, simply because this has been how they voted in the past eight elections [@blueredstate]. Out of the 51 states, there are 20 states which voted for the same party each time in the past nine elections and therefore there is a high probability that the pattern will be upheld with this year's election [@blueredstate]. On the other end of the spectrum, there are seven states which have voted for each party three of more times within the last nine elections——these would be the states of greater interest to us [@blueredstate].

Using the non-probability sampling method of quota sampling, these swing states will first be selected. This targetted sampling process allows us to focus our polling efforts on gathering more data from the areas where there is higher uncertainty, but the tradeoff is bias is easily introduced with the assumptions we are making, potentially impacting the accuracy of our forecast [@quotasampling]. This means that more work is required to adjust for these biases while also minimizing the inflation of variance [@quotasamping].

Next, within these states, probability proportionate to size will be used to select participants from the nationwide file of registered voters to ensure that the number of people polled is proportional to the number of voters per region. This is the sampling method used in @fox, as discussed above in @sec-pollster-analysis, and it allows for greater accuracy of prediction due to each unit's strategically adjusted probability of inclusion [@Latpate2021].

- questions (wording, order, options)
- treatment of non-response
- offer of incentive
